---
title: "Lab 2 Question Set"
author: "Hexiang Zhang"
date: "9/16/2019"
output: html_document
---

```{r}

choco <- read.csv("https://raw.githubusercontent.com/lbchu/ds202_labs/master/choco.csv")

```

### 1. How are ratings distributed? Don’t forget to mention outliers, if there are any.

```{r}

hist(choco$Rating, breaks = 20)

boxplot(choco$Rating)

```
   
These ratings look pretty normally distributed. From the boxplot, there are five outliers. Four outliers ranging between ratings of 0-1 and one outlier at rating 5.  

### 2. Do ratings depend on the cacao percentage of a chocolate bar?

```{r}

plot(Cocoa.Pct ~ Rating, data = choco) + abline(lm(Cocoa.Pct~Rating, data=choco))

```

   There does not appear to be a corrolation between the cacao percentage of a chocolate bar. The scatterplot  

### 3. What class is the variable representing company locations? How is this different from a ‘character’ variable? (You do not need to produce a graphic for this question.)

```{r} 

sapply(choco, class)

```

Company locations are factors. Factors store data into levels. Elements in factors take on a specific set of values. Factors can seem like character vectors, but factors are integers under the hood. 