---
title: "Lab 2"
author: "Ashley Anderson"
date: "9/12/2019"
output: html_document
---

```{r, results="hide"}
choco <- read.csv("https://raw.githubusercontent.com/lbchu/ds202_labs/master/choco.csv")
head(choco)
```

####Question Set - Individual 1

#####1.  
The chocolate ratings are approximately noramlly distributed, possibly slightly left skewed. From the boxplot, there appears to be a few outliers, namely one greater, and four less than the rest of the data. 

```{r}
hist(choco$Rating)
boxplot(choco$Rating)
```

#####2.  
It does not appear that there is a relationship between the rating of a chocolate bar and the chocolate bar's cocoa percentage in the scatterplot below.
```{r}
plot(choco$Cocoa.Pct,choco$Rating)
```

#####3.  
Company location is a factor variable. Character variables are categorical variables, while factor variables look like categorical variables but can also function like numeric because they have integers underneath the labels. 
```{r}
str(choco$Company.Location)
```

